\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-30 latex/paper_sensores/paper.tex
hice algunos cambios

\textbf{Experimental setup:} In order to perform the measures, a very simple experimental setup was developed: an adjustable table with a rotating plane (see Figures \ref{fig:mesa} and \ref{fig:mesa_esquema}).

@@

It is important to clarify that to perform a perfect temperature compensation, variations of temperatures should be produced with the sensors in different orientations. However, the one that is the most important is with the platform in horizontal position with the $z$ axis pointing ``up''. This is because this particular position is the main operating situation in the application for which this calibration method was thougth.
\section{Results and analysis}
\subsection{Static parameters}
In this section, the parameters that solve problem \ref{eq:calib_problem} are presented for both accelerometer and gyroscope. In addition, the statistic over the test set is studied and analyzed. \\

@@

It is interesting to compare the values obtained with the theoretical values of each parameter. As we can see, comparing the vector obtained with the seed, the values of the gains and the rotations are similar to what is declared in the datasheets. However the offset values obtained differ considerably from the information of the datasheet (see \cite{bib:acc_data}), where is declared that the 0g output is $\pm 150 mg$ for axes $x$ and $y$ and $\pm 250mg$ for axis $z$. This correspond to offsets of $39$ bits maximum for $x$ and $y$, and $64$ for $z$. The results obtained are consistent with what is declared in the datasheets.

@@

Last but not least, the results over the test set are the following:

@@

As can be seen the error obtained, in terms of bits, is bigger for the gyroscope than for the accelerometer. The main reason for this to happen is that in this case the scale of the experiment is far from optimal, yet the only one available, for the speed of interest. The maximal angular speed measured ($198 ^{\circ} /s$ ) is approximately a tenth of the scale of the gyroscope ($2000^{\circ} /s$) while for the accelerometer the maximal acceleration measured ($g$) is the half of the scale used ($2 g$).

@@

In Figure \refp{fig:bajada} two different magnitudes
are shown at the same time: the three projections of the acceleration and the
temperature vs. time, thus two axes are needed to be shown: on left side
the acceleration in $ms{−2}$, and on right side the temperature in
$^oC$.\\

>>>>

\textbf{Experimental setup:} In order to perform the measures, a very simple experimental setup was developed: an adjustable table with a rotating plane (see Figures \ref{fig:mesa} and \ref{fig:mesa_esquema}).\\

@@

It is important to clarify that to perform a perfect temperature compensation, variations of temperatures should be produced with the sensors in different orientations. However, the most important is that the platform is in horizontal position with the $z$ axis pointing ``up''. This is because this particular position is the main operating situation in the application for which this calibration method was thougth.
\section{Results and analysis}
\subsection{Static parameters}
In this section, the parameters that solve problem \ref{eq:calib_problem} are presented for both accelerometer and gyroscope. In addition, the statistic over the test set is studied and analyzed. \\

@@

It is interesting to compare the values obtained with the theoretical values of each parameter. As we can see, comparing the vector obtained with the seed, the values of the gains and the rotations are similar to what is declared in the datasheets. Furthermore, the offset values are also consistant with the information of the datasheet, yet this is not a straightforward conclusion, thus we present the following analyisis. In \cite{bib:acc_data} is declared that the $0g$ output is $\pm 150 mg$ for axes $x$ and $y$ and $\pm 250mg$ for axis $z$. This correspond to offsets of $39$ bits maximum for $x$ and $y$, and $64$ for $z$. Therefore, we can conclude that the results obtained are consistent with what is declared in the datasheets.

@@

Last but not least, the statistical results over the test set are the following:

@@

As can be seen the error obtained, in terms of bits, is bigger for the gyroscope than for the accelerometer. The main reason for this to happen is that in this case the scale of the experiment is far from optimal, yet the only one available in the sensor. The maximal angular speed measured ($198 ^{\circ} /s$ ) is approximately a tenth of the scale of the gyroscope ($2000^{\circ} /s$) while for the accelerometer the maximal acceleration measured ($g$) is the half of the scale used ($2 g$).

@@

In Figure \refp{fig:bajada} two different magnitudes
are shown at the same time: the three projections of the acceleration and the
temperature vs. time, thus two axes are needed to be shown: on left side
the acceleration in $ms^{-2}$, and on right side the temperature in
$^oC$.\\
